An Introduction to Rocker:\\ Docker Containers for R

### 2017-11-25 boettiger-eddelbuettel.Rmd
added ORCiD as suggested in proofreading-checklist

---
title: | 
       | An Introduction to Rocker: 
       | Docker Containers for R
author:
  - name: Carl Boettiger
    affiliation: UC Berkeley 
    address:
    - ESPM Department, University of California,
    - 130 Mulford Hall Berkeley, CA 94720-3114, USA
    email:  cboettig@berkeley.edu
  - name: Dirk Eddelbuettel
    affiliation: Debian and R Projects; Ketchum Trading
    address: 
    - Chicago, IL, USA
    email:  edd@debian.org
abstract: >
  We describe the Rocker project, which provides a widely-used suite of Docker images
  with customized R environments for particular tasks. We discuss how this suite is
  organized, and how these tools can increase portability, scaling, reproducibility,
  and convenience of R users and developers.
preamble: >
   \usepackage{longtable}
output: rticles::rjournal_article
---

>>>>

---
title: | 
       | An Introduction to Rocker: 
       | Docker Containers for R
author:
  - name: Carl Boettiger
    affiliation: UC Berkeley 
    address:
    - ESPM Department, University of California,
    - 130 Mulford Hall Berkeley, CA 94720-3114, USA
    - ORCiD \href{https://orcid.org/0000-0002-1642-628X}{0000-0002-1642-628X}
    email:  cboettig@berkeley.edu
  - name: Dirk Eddelbuettel
    affiliation: Debian and R Projects; Ketchum Trading
    address: 
    - Chicago, IL, USA
    - ORCiD \href{https://orcid.org/0000-0001-6419-907X}{0000-0001-6419-907X}
    email:  edd@debian.org
abstract: >
  We describe the Rocker project, which provides a widely-used suite of Docker images
  with customized R environments for particular tasks. We discuss how this suite is
  organized, and how these tools can increase portability, scaling, reproducibility,
  and convenience of R users and developers.
preamble: >
   \usepackage{longtable}
output: rticles::rjournal_article
---

### 2017-11-25 boettiger-eddelbuettel.tex
added ORCiD as suggested in proofreading-checklist

\address{%
Carl Boettiger\\
UC Berkeley\\
ESPM Department, University of California,\\ 130 Mulford Hall Berkeley, CA 94720-3114, USA\\
}
\href{mailto:cboettig@berkeley.edu}{\nolinkurl{cboettig@berkeley.edu}}

\address{%
Dirk Eddelbuettel\\
Debian and R Projects; Ketchum Trading\\
Chicago, IL, USA\\
}
\href{mailto:edd@debian.org}{\nolinkurl{edd@debian.org}}

>>>>

\address{%
Carl Boettiger\\
UC Berkeley\\
ESPM Department, University of California,\\ 130 Mulford Hall Berkeley, CA 94720-3114, USA\\ ORCiD \href{https://orcid.org/0000-0002-1642-628X}{0000-0002-1642-628X}\\
}
\href{mailto:cboettig@berkeley.edu}{\nolinkurl{cboettig@berkeley.edu}}

\address{%
Dirk Eddelbuettel\\
Debian and R Projects; Ketchum Trading\\
Chicago, IL, USA\\ ORCiD \href{https://orcid.org/0000-0001-6419-907X}{0000-0001-6419-907X}\\
}
\href{mailto:edd@debian.org}{\nolinkurl{edd@debian.org}}
